Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

All observation events and instrument responses are projected onto the
user defined geometry. Because residual hadronic background models can be subject
to significant uncertainties, background correction must be applied,
such as the ring or the field-of-view background techniques or
background measurements must be performed within, e.g. reflected regions~\citep{Berge07}.
Parts of the data with high associated IRF systematics must also be excluded by defining
a "safe" data range. These data reduction steps are performed by classes and functions
implemented in the gammapy.makers subpackage (see \ref{ssec:gammapy-makers}).

@@

\begin{itemize}
	\item \code{SpectralModel}: models to describe spectral shapes of sources,
	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources
	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
	      light and phase curves.
\end{itemize}

>>>>

All observation events and instrument responses are projected onto the
user defined geometry. Because residual hadronic background models can be subject
to significant uncertainties, background correction must be applied,
such as the ring or the field-of-view background techniques or
background measurements must be performed within, e.g. reflected regions~\citep{Berge07}.
Parts of the data with high associated IRF systematics must also be excluded by defining
a "safe" data range. These data reduction steps are performed by classes and functions
implemented in the \code{gammapy.makers} subpackage (see \ref{ssec:gammapy-makers}).

@@

\begin{itemize}
	\item \code{SpectralModel}: models to describe spectral shapes of sources,
	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources,
	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
	      light and phase curves.
\end{itemize}
